Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
reword - repetition in into

In this work, we propose the synthesis of \emph{safe} control algorithms for
LTI models taking into consideration the continuous dynamics of the plant, 
alongside the discrete dynamics of the controller and the effects of its 
implementation, as well as the hybrid elements that relate them.  
%% In this paper, we synthesize controllers for hybrid
%% closed-loop systems, i.e., software-implemented embedded controllers along
%% with a model of their physical environment (the plant), that are
%% \emph{safe}.
Due to the complexity of such systems, in this work we focus 
on linear models with known  implementation features (e.g., number of bits, fixed-point
arithmetic), and perform synthesis of safe digital controllers, a property often 
overlooked in feedback control synthesis, but which plays an important role 
in real-world systems.

>>>>

In this work, we propose the synthesis of \emph{safe} control algorithms for
LTI models taking into consideration the continuous dynamics of the plant, 
alongside the discrete dynamics of the controller and the effects of its 
implementation, as well as the hybrid elements that relate them.  
%% In this paper, we synthesize controllers for hybrid
%% closed-loop systems, i.e., software-implemented embedded controllers along
%% with a model of their physical environment (the plant), that are
%% \emph{safe}.
Due to the complexity of such systems, in this work we focus 
on linear models with known  implementation features (e.g., number of bits, fixed-point
arithmetic). We specify the safety requirement over the state space. This is a property often 
overlooked in feedback control synthesis, but which plays an important role 
in real-world systems.
